---
title: "Pitch Presentation for Covid-19 Visulization App"
subtitle: "Coursera Developing Data Products Course Project"
author: "Xiaohan Wang"
date: "12/16/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, echo = FALSE}
library(plotly)
library(dplyr)
library(ggplot2)
covid <- read.csv("covid_over_time.csv")

states <- unique(as.character(covid$state))
states <- sort(states)
```

## The covid 19 visualization app 
- Link: <https://xiaohanwang.shinyapps.io/Project_covid/>
- A Shiny app created in R environment
- Based on 2020 US Covid-19 data obtained from CDC

      - (Total cases, total death, new cases and new death per day 
      across 60 US states/regions)


*Overview of the dataset (selected variables):*
```{r, class.output="bg-success"}
head(covid[, c(1:3, 6, 8, 11), 8])
```


## Graph display options
- **Date Range**: select anywhere between 2020-01-22 and 2020-12-13
- **State/region**: select single or multiple states/regions
- **Refresh button**: click to update graph
<br />
<br />
*List of states/regions:*
```{r, class.output="bg-success"}
options(width = 60)
states
```

      
## Graph type
- Total cases (y axis) over time (x axis)
- New cases per day 
- Total death over time  
- New death per day 
- Total death-to-case ratio over time  
      
## Example graph (default):

*Total cases over time for states AK, AL and AR from 2020-01-22 to 2020-12-13:*
```{r plot, fig.align = "center", fig.height=4}
covid$submission_date <- as.Date(covid$submission_date, "%m/%d/%Y")
selection <- c("AK", "AL", "AR")
subdata <- covid[covid$state %in% selection,]
Theme <- theme(axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    legend.title = element_text(size = 14))

ggplot(subdata, aes(x = submission_date, y = tot_cases, color = state)) + 
                geom_line() + xlab("Date") + ylab("Total Cases") + Theme
```

**Thank you!**
